### 2021-05-05 doc/thesis/chapters/dsp.tex
update

\begin{figure}[!h]
  \centering
    \includegraphics[width=7cm]{img/fm-channel-baseband.png}
  \caption{Allocation of frequencies in an FM channel \cite{ref_fig_channel_freqs}}
  \label{fig_channel_baseband_freqs}
\end{figure}

@@

The mono audio stream is located between 30 Hz and 15 kHz.
This signal is built by the sum of the left and right audio channels.
%The lower limit at 30 Hz is to prevent the transmission of a direct current (DC) part, which would require a large amount of power in transmission.
%This effect is one of the downsides of amplitude modulation (AM), where the carrier is located at the channels' center frequeny and requires a high transmission power. % TODO: check this fact
The upper limit at 15 kHz is chosen to maintain a sufficient spacing to the first subcarrier.
For audio streaming, as in FM broadcasting, this is not a limitation, since it is unlikely to have frequencies higher than 15 kHz in an audio stream.
Also, this already reaches the upper limit of the human ears' bandwith, so higher spectral parts will not be heard anyway.

@@

The first subcarrier is allocated at an offset of 19 kHz from the center frequency.
It is also called the 'pilot tone', since it is a continuous signal.
The pilot tone is used to be able to demodulate the left and right channel of an audio signal correctly, to generate stereo audio.

@@

A signal that is constructed by the difference between left and right audio channel is modulated on a 38 kHz subcarrier.
This subcarrier is an integer multiple of 19 kHz for practical reasons.
However, the 38 kHz carrier is suppressed and thus not visible in the received spectrum.
It can still be recovered, since it is phase coherent with the 19 kHz pilot tone per definition.
The bandwidth for this difference-signal spans 15 kHz on either side of the subcarrier.
It is used to generate a stereo audio signal, in combination with the mono signal.
This process is explained into more detail in chapter \ref{sec_fm_sig_demod}.

@@

Considering all these parts in the spectrum, there is still bandwidth free to use, up to the maximum channel bandwitdh of 100 kHz in one sideband.
Because of that, additional services were added to the pure audio transmission, to provide additional data services and information.
Services that were implemented are the Data Radio Channel (DARC), which is mostly used in Japan and the USA, the Subsidary Communication Authorization (SCA) and the Radio Data System (RDS) \cite{ref_rohde_u_schwarz}.
Out of these, RDS is the most significant service in Europe.
It is used to transmit additional information about the channel, such as the radio stations' name, currently playing songs' title or traffic information.\\

>>>>

\begin{figure}[!h]
  \centering
    \includegraphics[width=9cm]{img/fm-channel-baseband.png}
  \caption{Allocation of frequencies in an FM channel \cite{ref_fig_channel_freqs}}
  \label{fig_channel_baseband_freqs}
\end{figure}

@@

The mono audio stream is located between 30 Hz and 15 kHz.
This signal is built by the sum of the left and right audio channels.
%The lower limit at 30 Hz is to prevent the transmission of a direct current (DC) part, which would require a large amount of power in transmission.
%This effect is one of the downsides of amplitude modulation (AM), where the carrier is located at the channels' center frequeny and requires a high transmission power. % TODO: check this fact
The upper limit at 15 kHz is chosen to maintain a sufficient spacing to the first subcarrier.

For audio streaming, as in FM broadcasting, this is not a limitation, since it is unlikely to have frequencies higher than 15 kHz in an audio stream.
Also, this already reaches the upper limit of the human ears' bandwith, so higher spectral parts will not be heard anyway.

@@

The first subcarrier is allocated at an offset of 19 kHz from the center frequency.
This subcarrier is also called the 'pilot tone', since it is a continuous signal.
It is independent of any varying message signal content.
The pilot tone is used for stereo audio demodulation.
To regenerate a stereo audio signal, the left and right audio channels need to be recovered correctly.

@@

A signal that is constructed by the difference between the left and right audio channel is modulated on a 38 kHz subcarrier.
This subcarrier is an integer multiple of the pilot tone at 19 kHz, for practical reasons.
However, the 38 kHz carrier is suppressed and thus not visible in the received spectrum.
The modulation technique that is used for this spectral part is called dual-sideband suppressed-carrier (DSB-SC).
Even though the carrier is suppressed, it can still be recovered, because it is phase coherent with the 19 kHz pilot tone per definition.

The bandwidth for this difference-signal spans 15 kHz on either side of the subcarrier.
It is used to generate a stereo audio signal, in combination with the mono signal.
This process is explained into more detail in chapter \ref{sec_fm_sig_demod}.

@@

Considering all these parts in the spectrum, there is still free bandwidth available to use up to the maximum channel bandwitdh of 100 kHz in one sideband.
Because of that, additional services were added to the pure audio transmission, to provide additional data services and information.

Services that were implemented are the Data Radio Channel (DARC), which is mostly used in Japan and the USA, the Subsidary Communication Authorization (SCA) and the Radio Data System (RDS) \cite{ref_rohde_u_schwarz}.
Out of these, RDS is the most significant service in Europe.
It is used to transmit additional information about the channel, such as the radio stations' name, the currently playing songs' title or traffic information.\\
